Compositional Certified Resource Bounds

### 2014-07-03 paper/main.tex
fix Relax proof

\begin{lemma}[Relax]
  If $Q' \succeq_\Gamma Q$ and $\state$ is a program state such that
  $\state \models \Gamma$ then we have $\Phi_{Q'}(\state) \ge \Phi_Q(\state)$.
\end{lemma}
\begin{proof}
We observe the following inequations.
\begin{align*}
\Phi_{Q'}(\state) &= \sum_i q'_i f_i(H) \\
&\ge q_0 + \sum_{i\in\mathcal U} u_i p_i - \sum_{i\in\mathcal L} l_i p_i
  + \sum_{i\in\mathcal U} (q_i - p_i) f_i(bH)  \\ & \;\;\;\;\;\;\;\; + \sum_{i\in\mathcal L} (q_i + p_i) f_i(H)
  + \sum_{i\not\in \mathcal U \cup \mathcal L} q_i \\
 &\ge \Phi_Q(\state)
  + \sum_{i\in\mathcal U} (u_i - f_i(H)) p_i
  + \sum_{i\in\mathcal L} (f_i(H) - l_i) p_i \\
 &\ge \Phi_Q(\state).
\end{align*}
Since $H \models \Gamma$, using the transitivity of $\models$ and
the definition of $\mathcal U$ and $\mathcal L$ we get
$\forall i\in\mathcal L.\, l_i \le f_i(H)$ and
$\forall i\in\mathcal U.\, f_i(H)\le u_i$.
These two inequalities justify the last step.
\end{proof}
%
\noindent
We prove similar lemmas for the rules that deal with assignment.  With
the computational content of the proof, we have an effective algorithm
to construct certificates for upper bounds derived automatically.

>>>>

\begin{lemma}[Relax]
  If $Q' \succeq_\Gamma Q$ and $\state$ is a program state such that
  $\state \models \Gamma$ then we have $\Phi_{Q'}(\state) \ge \Phi_Q(\state)$.
\end{lemma}
\begin{proof}
We observe the following inequations.
\begin{align*}
\Phi_{Q'}(\state) &= \sum_i q'_i f_i(\state) \\
&\ge q_0 + \sum_{i\in\mathcal U} u_i p_i - \sum_{i\in\mathcal L} l_i p_i
  + \sum_{i\in\mathcal U} (q_i - p_i) f_i(\state)  \\ &
  \;\;\;\;\;\;\;\; + \sum_{i\in\mathcal L} (q_i + p_i) f_i(\state)
  + \sum_{i\not\in \mathcal U \cup \mathcal L} q_i \\
 &\ge \Phi_Q(\state)
  + \sum_{i\in\mathcal U} (u_i - f_i(\state)) p_i
  + \sum_{i\in\mathcal L} (f_i(\state) - l_i) p_i \\
 &\ge \Phi_Q(\state).
\end{align*}
Since $\state \models \Gamma$, using the transitivity of $\models$ and
the definition of $\mathcal U$ and $\mathcal L$ we get
$\forall i\in\mathcal L.\, l_i \le f_i(\state)$ and
$\forall i\in\mathcal U.\, f_i(\state)\le u_i$.
These two inequalities justify the last step.
\end{proof}
%
\noindent
We prove similar lemmas for the rules that deal with assignment.  With
the computational content of the proof, we have an effective algorithm
to construct certificates for upper bounds derived automatically.
